{{< pagebreak >}}
## Attenuation Decay

In this work, we will use a simulated data set (details given later) to study a physical model "attenuation decay".

### Physical Model
::: {.callout-note icon=false}
### Physical Model: Radiation strength measured at distance $x$

$$y = e^{-\lambda x}$$ 

- Response variable: $y=$ radiation strength
- Explanatory variable (numeric): $x=$ distance
- Parameter of interest: $\lambda =$ attenuation coefficient.
- Estimator: $\hat{\lambda} = -\frac{1}{x}\ln y$

Goal: Estimate the parameter $\lambda$ and its standard error
:::

We treat the parameter $\lambda$ as a random variable and follows a normal distribution. By central limit theorem (CLT), the sample mean of a random sample with sample size $n$ is also distributed normally:

$$
\begin{aligned}
\lambda_i &\overset{iid}{\sim} N(\mu, \sigma^2) \\
\Rightarrow
\bar{\lambda} &= \frac{1}{n} \sum_{i=1}^n \lambda_i \sim N(\mu, \sigma^2/n)
\end{aligned}
$$

### Data

Load the data set:

```{r}
# load session image
load(here("data", "sim_decay.RData"))
```

The data set contains `r n` observations of the radiation strength and measurement distance:

```{r}
# exam data set
df %>% select(y, x)

# scatter plot between measured strength y and distance x
plot(df$x, df$y, xlab = "x (distance)", ylab = "y (measured radiation strength)")
```

It's clearly to see the decay trend described in the physical model (the decay equation) and the randomness due to the uncertainty of the model parameter.
